Estimating Neighborhood Rents with Scraped Data

### 2018-06-15 manuscript/index.Rmd
fixing notation for models

Model                    | Abbr.   | Formula
------------------------ | ------- | ----------------------------------------------
Fixed Intercept          | `int`     | $\theta_{it} = \beta_0 + Qtr$
Non-Spatial              | `ns`      | $\theta_{it} = \beta_0 + \epsilon_i + Qtr$
Non-Spatial AR(1)        | `nsar1`  | $\theta_{it} = \beta_0 + \epsilon_t + \epsilon_{t-1} + \epsilon_i$
BYM Spatial AR(1)        | `bym `    | $\theta_{it} = \beta_0 + \epsilon_t + \epsilon_{t-1} + \epsilon_i + S_i.$
BYM Spatiotemporal AR(1) | `spt`     | $\theta_{it} = \beta_0 + \epsilon_t + \epsilon_{t-1} + \epsilon_i + S_i. + \epsilon_{it}$

The Fixed Intercept model (`int`) uses fixed effects for quarters only. The Non-Spatial (`ns`) model adds random noise (i.i.d.) tract random-effects. The Non-Spatial AR(1) model (`nsar1`) uses AR(1) process to model the temporal dynamics (formally, $\epsilon_1 \sim \mbox{Normal}(0, (\tau(1-\rho^2))^{-1}))$ where $\epsilon_t = \rho x_{t-1} + \epsilon_t$). This model includes a random noise term for each quarter too.

>>>>

Model                    | Abbr.   | Formula
------------------------ | ------- | ----------------------------------------------
Fixed Intercept          | `int`     | $\theta_{it} = \beta_0 + Qtr$
Non-Spatial              | `ns`      | $\theta_{it} = \beta_0 + \epsilon_i + Qtr$
Non-Spatial AR(1)        | `nsar1`  | $\theta_{it} = \beta_0 + x_t + \epsilon_t + \epsilon_i$
BYM Spatial AR(1)        | `bym `    | $\theta_{it} = \beta_0 + x_t + \epsilon_t  + \epsilon_i + S_i.$
BYM Spatiotemporal AR(1) | `spt`     | $\theta_{it} = \beta_0 + x_t + \epsilon_t  + \epsilon_i + S_i + \epsilon_{it}$

The Fixed Intercept model (`int`) uses fixed effects for quarters only. The Non-Spatial (`ns`) model adds random noise (i.i.d.) tract random-effects. The Non-Spatial AR(1) model (`nsar1`) uses AR(1) process to model the temporal dynamics (formally, $x_1 \sim \mbox{Normal}(0, (\tau(1-\rho^2))^{-1})$ where $x_t = \rho x_{t-1} + \epsilon_t$). This model includes a random noise term for each quarter too.
